A sensor grid approach for large scale acoustic monitoring

### 2017-06-22 paper/article.tex
Commit clean
inteligibility

Intelligibility in decoded and reconstructed audio is also oan concerns of this study. It is indeed important that the produced scheme maintains a high level of recognition of acoustic events but, as the dat is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.

@@

We thus provide the computation of two objective metrics: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio. These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.\\

>>>>

Intelligibility in decoded and reconstructed audio is also an important concern in this study. It is indeed important that the proposed scheme ensures a high level of recognition of acoustic events but, as the data is transmitted over the network and potentially stored, the level of intelligibility of the decoded stream should be as low as possible.

Forensic phonetics \cite{baldwin1990forensic}

indice biométrique faible \cite{boe2000forensic}

In order to decrease the intelligibility, several approaches can be considered. First,  a speech versus non speech detector can be implemented on the sensor. If some speech is detected, the data is not transmitted. This approach is prone to failure of the detector and will lead to unavailibility of data whcih might compromise the computation of some indicators. Second, as the speech is mostly concentrated at a given frequency region, a band pass filter from 1 kHz to $~$4-5 kHz could be considered in order to remove the formant information \cite{kent1992acoustic}. However, as some frequency bands are no longer available, the computation of the acoustic indicators is no longer possible. A third approach is to wisely choose the frame rate. Since a phoneme is about 100ms to 200ms long \cite{kuwabara1996acoustic} \cite{rosen1992temporal} a frame rate lower than 4 Hz should dramatically reduce intelligibility.

@@

To evaluate the impact of the frame rate on intelligibility two objective metrics are considered: the Coherence Speech Intelligibility Index\cite{kates2005} (CSII) and frequency-weighted segmental SNR\cite{hu2008} (fwSNRseg) by comparing original unaltered samples and recovered audio. These two indicators have been shown to correlate well with perceptual tests\cite{ma2009}, although results are only available for lesser degradations and distortions than the ones we consider in this study.\\
